---
title: "supervised brain--behavior analysis"
author: "michael freund"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: spacelab
    highlight: zenburn
---
  
  
```{r setup, include = FALSE}

knitr::opts_chunk$set(
  fig.align = 'center', fig.fullwidth = TRUE
)

source(here::here("code", "_packages.R"))
source(here("code", "read-behav.R"))
source(here("code", "_vars.R"))
source(here("code", "_atlases.R"))
source(here("code", "_settings.R"))
source(here("code", "_funs.R"))

er.sum <- fread(here("out", "behav_sumstat_error.csv"))
rt.sum <- fread(here("out", "behav_sumstat_rt.csv"))


a <- readRDS(here("out", "roistats_hilo_target_2trpk_unshifted.RDS"))
is.missing.fmri <- apply(a, 1, function(x) any(is.na(x)))
subjs.missing.fmri <- names(is.missing.fmri)[is.missing.fmri]

is.complete.behav <- 
  rowSums(with(axcpt, table(subj, session)) > 0) > 2 &
  rowSums(with(cuedts, table(subj, session)) > 0) > 2 &
  rowSums(with(stern, table(subj, session)) > 0) > 2 &
  rowSums(with(stroop, table(subj, session)) > 0) > 2
subjs.missing.behav <- names(is.complete.behav)[!is.complete.behav]

subjs.missing <- union(subjs.missing.fmri, subjs.missing.behav)
subjs.complete <- sort(setdiff(subjs, c(subjs.missing, "197449")))

a <- a[subjs.complete, , , ]

rt.sum <- rt.sum[subj %in% subjs.complete]
er.sum <- er.sum[subj %in% subjs.complete]


cm.sum <- bind_cols(
  rt.sum %>% arrange(task, subj) %>% select(task, subj),
  er.sum %>% group_by(task) %>% mutate(across(where(is.numeric), function(x) c(scale(x)))) %>% arrange(task, subj) %>%
    .[c("baseline", "proactive", "reactive")] +
  rt.sum %>% group_by(task) %>% mutate(across(where(is.numeric), function(x) c(scale(x)))) %>% arrange(task, subj) %>%
    .[c("baseline", "proactive", "reactive")]
)

```


* Subjects: `r length(subjs.complete)` included
* INCLUDES TWINS


Purpose:

* predict behavioral effect of control demand (hi/lo contrast) with multivariate model
* models use parcel means as explanatory variables, explaining hi/lo behavioral contrast
* ridge regression used, with 5-fold crossvalidation to tune lambda
* models fitted to different subsets of predictors: schaefer networks


# glance at group-level

* look at mahalanobis distances (from centroid) to ID outliers
* in MVN, mahalanobis^2 are chi-square distributed with df = number dimensions

```{r fig.width = 7, results = FALSE}

## multivariate outliers?

mahal <- apply(a, c("task", "session"), function(x) mahalanobis(x, center = colMeans(x), cov = cov.shrink(x)))
mahal %>%
  reshape2::melt() %>%
  ggplot(aes(sample = value)) +
  
  stat_qq(distribution = qchisq, dparams = list(df = 400)) +
  stat_qq_line(distribution = qchisq, dparams = list(df = 400)) +
  facet_grid(vars(task), vars(session)) +
  
  labs(title = "mahalanobis^2 against chisq")


b.pvals <- apply(
  a, c("task", "session", "parcel"), function(x) wilcox.test(x, alternative = "greater")$p.value
  ) %>%
  apply(c("task", "session"), p.adjust, "fdr") %>% reshape2::melt()


b.pvals %>% filter(value < 0.05) %>% with(., table(task, session)) / 4 ## percent of parcels significantly activated

```


## profiles

### all parcels

```{r fig.height = 10}

means <- a %>% 
  apply(c("task", "parcel", "session"), mean) %>% 
  reshape2::melt()
means$network <- get.network(means$parcel)

means %>%
  
  ggplot(aes(parcel, value, color = task, group = task)) +
  
  geom_line(size = 1) +
  scale_color_brewer(type = "qual", palette = 2) +
  facet_grid(vars(session)) +
  
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 3), legend.position = "top") +
  labs(title = "task profile across parcels", y = "mean beta")

means %>%
  
  group_by(task, session) %>%
  mutate(value = scale(value)) %>%
  
  ggplot(aes(parcel, value, color = task, group = task)) +
  
  geom_line(size = 1) +
  scale_color_brewer(type = "qual", palette = 2) +
  facet_grid(vars(session)) +
  
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 3), legend.position = "top") +
  labs(title = "task profile across parcels", y = "mean beta  (z-scored across parcels w/n task)")


```



### FPN, CON, DAN

```{r fig.height = 10}

means %>%
  
  filter(network %in% c("Cont", "SalVentAttn", "DorsAttn")) %>%
  
  ggplot(aes(parcel, value, color = task, group = task)) +
  
  geom_hline(yintercept = 0) +
  geom_line(size = 1) +
  
  scale_color_brewer(type = "qual", palette = 2) +
  facet_wrap(vars(session, network), nrow = 3, scales = "free_x") +
  
  theme(axis.text.x = element_blank(), legend.position = "top") +
  labs(title = "task profile across parcels | assoc networks", y = "mean beta")



means %>%
  
  filter(network %in% c("Cont", "SalVentAttn", "DorsAttn")) %>%
  
  group_by(task, session) %>%
  mutate(value = scale(value)) %>%
  
  ggplot(aes(parcel, value, color = task, group = task)) +
  
  geom_line(size = 1) +
  scale_color_brewer(type = "qual", palette = 2) +
  facet_wrap(vars(session, network), nrow = 3, scales = "free_x") +
  
  theme(axis.text.x = element_blank(), legend.position = "top") +
  labs(title = "task profile across parcels | assoc networks", y = "mean beta (z-scored across parcels w/n task)")


```



### DMCC34

```{r fig.height = 10}

means %>%
  
  filter(parcel %in% parcellation$key[dmcc34]) %>%
  
  ggplot(aes(parcel, value, color = task, group = task)) +
  
  geom_hline(yintercept = 0) +
  geom_line(size = 1) +
  
  scale_color_brewer(type = "qual", palette = 2) +
  facet_grid(vars(session)) +
  
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "task profile across parcels | DMCC34", y = "mean beta")



means %>%
  
  filter(parcel %in% parcellation$key[dmcc34]) %>%
  
  group_by(task, session) %>%
  mutate(value = scale(value)) %>%
  
  ggplot(aes(parcel, value, color = task, group = task)) +
  
  geom_hline(yintercept = 0) +
  geom_line(size = 1) +
  
  scale_color_brewer(type = "qual", palette = 2) +
  facet_grid(vars(session)) +
  
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "task profile across parcels | DMCC34", y = "mean beta (z-scored across parcels w/n task)")


```





# brain--behavior: across task, within session

## RT

```{r fig.width = 7, fig.height = 3}

## subset training set

cv.task <- function(X, Y) {
  # X <- a; Y <- rt.sum
  
  X <- X %>% apply(c("task", "subj", "session"), function(x) scale(x))
  X <- aperm(X, c(3, 1, 2, 4))
  # print(dim(X))
  
  res <- setNames(vector("list", length(sessions)), sessions)
  Y %<>% arrange(task, subj)  ## sort
  
  set.seed(0)
  for (session.i in sessions) {
    # session.i <- "baseline"
    
    Xses <- X[, , , session.i]
    M <- matrix(NA, ncol = 4, nrow = 4, dimnames = list(train = tasks, test = tasks))
    
    for (task.train in tasks) {
      # task.train = "Axcpt"
      
      Y_train <- Y[task %in% task.train]
      X_train <- Xses[, , task.train]
      
      ## make sure in same order:
      if (!identical(Y_train$subj, dimnames(X_train)$subj)) stop("subjs not aligned train")
      
      yhat_train <- rep(NA, length(subjs.complete))
      yhat_test  <- matrix(
        NA, ncol = 3, nrow = length(subjs.complete), 
        dimnames = list(subj = subjs.complete, task = setdiff(tasks, task.train))
        )
      
      # fitcv <- cv.glmnet(X_train, y_train, alpha = 0)  ## for tuning lambda
      # fit <- glmnet(X_train, y_train, alpha = 0, lambda = fitcv$lambda.min)  ## for generating predictions
      
      Xs_train <- scale(X_train)
      Ys_train <- scale(Y_train[[session.i]])
      
      for (subj.test in seq_along(subjs.complete)) {
        # subj.test = 1
        
        # Xs_train <- X_train[-subj.test, ]
        # ys_train <- Y_train[[session.i]][-subj.test]
        
        Xs_train <- X_train[-subj.test, ]
        ys_train <- Ys_train[-subj.test]
        # mu <- colMeans(X_train[-subj.test, ])
        # sdev <- apply(X_train[-subj.test, ], 2, sd)
        
        fit <- glmnet(Xs_train, ys_train, alpha = 0, lambda = 5:1)  ## for generating predictions
        yhat_train[subj.test] <- 
          c(
            predict(
              fit, 
              newx = X_train[subj.test, , drop = FALSE],
              #sweep(X_train[subj.test, , drop = FALSE] - mu, 2, sdev, "/"), ## scale newx to training set
              s = 1
            )
          )
        
        for (task.i in setdiff(tasks, task.train)) {
          # task.i = "Cuedts"
          
          Y_test <- Y[task %in% task.i]
          X_test <- scale(Xses[, , task.i])
          
          ## make sure in same order:
          if (!identical(Y_test$subj, dimnames(X_test)$subj)) stop("subjs not aligned test")
          
          yhat_test[subj.test, task.i] <- 
            c(
              predict(
                fit, 
                newx = scale(X_test)[subj.test, , drop = FALSE],
                #sweep(X_test[subj.test, , drop = FALSE] - mu, 2, sdev, "/"), ## scale newx to training set
                s = 1
              )
            )

        }

      }
      
      r_train <- cor(Y_train[task == task.train][[session.i]], yhat_train)
      r_test <- cor(Y_test[task == task.i][[session.i]], yhat_test)
      
      M[task.train, task.train] <- r_train
      M[task.train, setdiff(tasks, task.train)] <- r_test
      
    }
    
    if (any(is.na(c(M)))) stop("NA")
    
    res[[session.i]] <- M
      
  }
  
  res

}


confusion.task.allparc <- cv.task(a[, !get.network(parcellation$key) %in% "Limbic", , ], rt.sum)
confusion.task.fpn     <- cv.task(a[, get.network(parcellation$key) == "Cont", , ], rt.sum)
confusion.task.con     <- cv.task(a[, get.network(parcellation$key) == "SalVentAttn", , ], rt.sum)
confusion.task.ctrl    <- cv.task(a[, get.network(parcellation$key) %in% c("Cont", "SalVentAttn"), , ], rt.sum)
confusion.task.dmcc34  <- cv.task(a[, parcellation$key[dmcc34], , ], rt.sum)
confusion.task.smv     <- cv.task(a[, get.network(parcellation$key) %in% c("SomMot", "Vis"), , ], rt.sum)


confusion.task.allparc %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), RT, allparcs", x = "train", y = "test")


confusion.task.fpn %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), RT, FPN", x = "train", y = "test")


confusion.task.con %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), RT, CON", x = "train", y = "test")


confusion.task.ctrl %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), RT, FPN+CON", x = "train", y = "test")


confusion.task.dmcc34 %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), RT, DMCC34", x = "train", y = "test")




confusion.task.smv %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), RT, SM+Vis", x = "train", y = "test")

```



## ER

```{r fig.width = 7, fig.height = 3}

confusion.task.allparc <- cv.task(a[, !get.network(parcellation$key) %in% "Limbic", , ], er.sum)
confusion.task.fpn <- cv.task(a[, get.network(parcellation$key) == "Cont", , ], er.sum)
confusion.task.con <- cv.task(a[, get.network(parcellation$key) == "SalVentAttn", , ], er.sum)
confusion.task.ctrl <- cv.task(a[, get.network(parcellation$key) %in% c("Cont", "SalVentAttn", "DorsAttn"), , ], er.sum)
confusion.task.dmcc34 <- cv.task(a[, parcellation$key[dmcc34], , ], er.sum)
confusion.task.smv <- cv.task(a[, get.network(parcellation$key) %in% c("SomMot", "Vis"), , ], er.sum)


confusion.task.allparc %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), ER, allparcs", x = "train", y = "test")


confusion.task.fpn %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), ER, FPN", x = "train", y = "test")


confusion.task.con %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), ER, CON", x = "train", y = "test")


confusion.task.ctrl %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +

  labs(title = "cor(y, yhat), ER, FPN+CON", x = "train", y = "test")


confusion.task.dmcc34 %>%
    
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +

  labs(title = "cor(y, yhat), ER, DMCC34", x = "train", y = "test")



confusion.task.smv %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), ER, SM+Vis", x = "train", y = "test")

```


## composite

```{r fig.width = 7, fig.height = 3}

confusion.task.allparc <- cv.task(a[, !get.network(parcellation$key) %in% "Limbic", , ], cm.sum)
confusion.task.fpn <- cv.task(a[, get.network(parcellation$key) == "Cont", , ], cm.sum)
confusion.task.con <- cv.task(a[, get.network(parcellation$key) == "SalVentAttn", , ], cm.sum)
confusion.task.ctrl <- cv.task(a[, get.network(parcellation$key) %in% c("Cont", "SalVentAttn"), , ], cm.sum)
confusion.task.dmcc34 <- cv.task(a[, parcellation$key[dmcc34], , ], cm.sum)
confusion.task.smv <- cv.task(a[, get.network(parcellation$key) %in% c("SomMot", "Vis"), , ], cm.sum)


confusion.task.allparc %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), ER+RT, allparcs", x = "train", y = "test")


confusion.task.fpn %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), ER+RT, FPN", x = "train", y = "test")


confusion.task.con %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), ER+RT, CON", x = "train", y = "test")


confusion.task.ctrl %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +

  labs(title = "cor(y, yhat), ER+RT, FPN+CON", x = "train", y = "test")


confusion.task.dmcc34 %>%
    
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +

  labs(title = "cor(y, yhat), ER+RT, DMCC34", x = "train", y = "test")



confusion.task.smv %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "session") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(session)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  
  labs(title = "cor(y, yhat), ER+RT, SM+Vis", x = "train", y = "test")

```





# brain--behavior: across session, within task

## RT

```{r fig.width = 7, fig.height = 2.75}



cv.sess <- function(X, Y) {
  
  # X <- X %>% apply(c("task", "subj", "session"), function(x) scale(x))
  # X <- aperm(X, c(3, 1, 2, 4))
  # print(dim(X))
  
  res <- setNames(vector("list", length(tasks)), tasks)
  
  set.seed(0)
  for (task.i in tasks) {
    # task.i <- "Axcpt"
    
    M <- matrix(NA, ncol = 3, nrow = 3, dimnames = list(train = sessions, test = sessions))
    
    for (sess.train in sessions) {
      # sess.train = "reactive"
      
      X_train <- X[, , task.i, sess.train]
      y <- Y[task %in% task.i]
    
      ## make sure in same order:
      
      X_train <- scale(X_train[y$subj, ])
      y_train <- scale(y[[sess.train]])
      
      # fitcv <- cv.glmnet(X_train, y_train, alpha = 0)  ## for tuning lambda
      # fit <- glmnet(X_train, y_train, alpha = 0, lambda = fitcv$lambda.min)  ## for generating predictions
      # yhat_train <- c(predict(fit, newx = X_train))
      fit <- glmnet(X_train, y_train, alpha = 0, lambda = 3:1)  ## for generating predictions
      yhat_train <- c(predict(fit, newx = X_train, s = 1))
      r_train <- cor(y_train, yhat_train)
      
      M[sess.train, sess.train] <- r_train
      
      for (session.i in setdiff(sessions, sess.train)) {
        # session.i = "proactive"
        
        ## test
        
        y_test <- Y[task %in% task.i]
        X_test <- X[, , task.i, session.i]
        X_test <- scale(X_test[y_test$subj, ])  ## same order
        
        yhat_test <- c(predict(fit, newx = X_test, s = 1))
        # if (isTRUE(all.equal(var(yhat_test), 0))) next
        r_test <- cor(y_test[[session.i]], yhat_test)
        
        M[sess.train, session.i] <- r_test
        
        
      }
      
    }
    
    res[[task.i]] <- M
    
  }
  
  res

}


confusion.sess.allparc <- cv.sess(a[, !get.network(parcellation$key) %in% "Limbic", , ], rt.sum)
confusion.sess.fpn     <- cv.sess(a[, get.network(parcellation$key) == "Cont", , ], rt.sum)
confusion.sess.con     <- cv.sess(a[, get.network(parcellation$key) == "SalVentAttn", , ], rt.sum)
confusion.sess.ctrl    <- cv.sess(a[, get.network(parcellation$key) %in% c("Cont", "SalVentAttn"), , ], rt.sum)
confusion.sess.dmcc34  <- cv.sess(a[, parcellation$key[dmcc34], , ], rt.sum)
confusion.sess.smv     <- cv.sess(a[, get.network(parcellation$key) %in% c("SomMot", "Vis"), , ], rt.sum)


confusion.sess.allparc %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), RT, allparcs", x = "train", y = "test")



confusion.sess.fpn %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), RT, FPN", x = "train", y = "test")



confusion.sess.con %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), RT, CON", x = "train", y = "test")



confusion.sess.ctrl %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), RT, FPN+CON", x = "train", y = "test")


confusion.sess.dmcc34 %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), RT, dmcc34", x = "train", y = "test")


confusion.sess.smv %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), RT, SomMot+Vis", x = "train", y = "test")



```


## ER

```{r fig.width = 7, fig.height = 2.75}

confusion.sess.allparc <- cv.sess(a[, !get.network(parcellation$key) %in% "Limbic", , ], er.sum)
confusion.sess.fpn     <- cv.sess(a[, get.network(parcellation$key) == "Cont", , ], er.sum)
confusion.sess.con     <- cv.sess(a[, get.network(parcellation$key) == "SalVentAttn", , ], er.sum)
confusion.sess.ctrl    <- cv.sess(a[, get.network(parcellation$key) %in% c("Cont", "SalVentAttn"), , ], er.sum)
confusion.sess.dmcc34  <- cv.sess(a[, parcellation$key[dmcc34], , ], er.sum)
confusion.sess.smv     <- cv.sess(a[, get.network(parcellation$key) %in% c("SomMot", "Vis"), , ], er.sum)


confusion.sess.allparc %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER, allparcs", x = "train", y = "test")



confusion.sess.fpn %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER, FPN", x = "train", y = "test")



confusion.sess.con %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER, CON", x = "train", y = "test")



confusion.sess.ctrl %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER, FPN+CON", x = "train", y = "test")


confusion.sess.dmcc34 %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER, dmcc34", x = "train", y = "test")


confusion.sess.smv %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER, SomMot+Vis", x = "train", y = "test")



```



## composite

```{r fig.width = 7, fig.height = 2.75}

confusion.sess.allparc <- cv.sess(a[, !get.network(parcellation$key) %in% "Limbic", , ], cm.sum)
confusion.sess.fpn     <- cv.sess(a[, get.network(parcellation$key) == "Cont", , ], cm.sum)
confusion.sess.con     <- cv.sess(a[, get.network(parcellation$key) == "SalVentAttn", , ], cm.sum)
confusion.sess.ctrl    <- cv.sess(a[, get.network(parcellation$key) %in% c("Cont", "SalVentAttn"), , ], cm.sum)
confusion.sess.dmcc34  <- cv.sess(a[, parcellation$key[dmcc34], , ], cm.sum)
confusion.sess.smv     <- cv.sess(a[, get.network(parcellation$key) %in% c("SomMot", "Vis"), , ], cm.sum)


confusion.sess.allparc %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER+RT, allparcs", x = "train", y = "test")



confusion.sess.fpn %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER+RT, FPN", x = "train", y = "test")



confusion.sess.con %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER+RT, CON", x = "train", y = "test")



confusion.sess.ctrl %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER+RT, FPN+CON", x = "train", y = "test")


confusion.sess.dmcc34 %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER+RT, dmcc34", x = "train", y = "test")


confusion.sess.smv %>%
  
  lapply(symmat4ggplot) %>%
  bind_rows(.id = "task") %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2))) +
  
  facet_grid(cols = vars(task)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("BAS", "PRO", "REA")) +
  scale_y_discrete(labels = c("BAS", "PRO", "REA") %>% rev) +
  geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = 0.5, ymax = 2.5), fill = "transparent", color = "black", size = 2) +
  
  labs(title = "cor(y, yhat), ER+RT, SomMot+Vis", x = "train", y = "test")


```


