---
title: "behavioral QC analyses"
author: "michael freund"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: spacelab
    highlight: zenburn
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(
  fig.align = 'center', fig.fullwidth = TRUE, cache = TRUE
)

source(here::here("code", "_packages.R"))
source(here("code", "read-behav.R"))
source(here("code", "_vars.R"))
source(here("code", "_atlases.R"))
source(here("code", "_settings.R"))

```


# about

* list for each task*session for subjs or trials to exclude
* estimate behavioral effects


# My notes from basecamp thread

* 161832 is one i've excluded from my analyses. high error rates in stroop (>10%, many omissions) in Bas and Pro, and in other tasks.
* DMCC3128324 axcpt 2nd run ~40% errors. would be one to check if they were indeed responding (or were asleep), motion levels, etc.
* 203418: 80% of the responses were incorrect in AXCPT. guessing this is a response-mapping issue (i.e., they got the buttons mixed up). if it were up to me i'd exclude bc it's hard to verify what instructions they were following (and on which trials).
* 448347: generally high error rate; would be one to check whether they seem to be sleeping (they may just be bad at the tasks).
* 580650: axcpt run 2, 16% of frames censored (FD>0.9)
* DMCC1328342: stroop run 1, 10% frames censored, mean(FD) = 0.6
* 849971: cluster of stroop RTs that look like they may be due to that audio signal artifact. (right around 500 ms, very low variance, clear deviance in QQ plot). not suggesting tossing this subj, but just excluding those RT measurements.
* DMCC8260571


# complete cases (subjects)

```{r}

a <- readRDS(here("out", "roistats_hilo_target_2trpk_unshifted.RDS"))
is.missing.fmri <- apply(a, 1, function(x) any(is.na(x)))
subjs.missing.fmri <- names(is.missing.fmri)[is.missing.fmri]

is.complete.behav <- 
  rowSums(with(axcpt, table(subj, session)) > 0) > 2 &
  rowSums(with(cuedts, table(subj, session)) > 0) > 2 &
  rowSums(with(stern, table(subj, session)) > 0) > 2 &
  rowSums(with(stroop, table(subj, session)) > 0) > 2
subjs.missing.behav <- names(is.complete.behav)[!is.complete.behav]

subjs.missing <- union(subjs.missing.fmri, subjs.missing.behav)

subjs.missing
length(subjs.missing)

subjs.complete <- setdiff(subjs, subjs.missing)
subjs.complete
length(subjs.complete)

```



# errors

```{r}

axcpt.er <- axcpt %>% filter(!subj %in% names(is.missing.fmri)[is.missing.fmri])

axcpt.er %>%
  
  group_by(subj, session) %>%

  mutate(
    cue.o = as.numeric(is.na(cue.resp)),
    cue.c = ifelse(is.na(cue.resp), 0, 1 - acc),
    target.o = ifelse(is.na(target.cresp), 0, as.numeric(is.na(target.resp))),
    target.c = ifelse(is.na(target.resp), 0, 1 - acc)
    ) %>%
  
  summarize(across(c("cue.o", "cue.c", "target.o", "target.c"), mean)) %>%
  
  reshape2::melt() %>%
  ggplot(aes(subj, value, fill = variable)) +
  
  geom_col(position = position_dodge(width = 0.5), width = 0.5) +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "axcpt")





cuedts.er <- cuedts %>% filter(!subj %in% names(is.missing.fmri)[is.missing.fmri])

cuedts.er %>%
  
  group_by(subj, session) %>%
  
  mutate(
    er.o = as.numeric(is.na(resp)),
    er.c = ifelse(is.na(resp), 0, 1 - acc)
    ) %>%
  
  summarize(across(c("er.o", "er.c"), mean)) %>%
  
  reshape2::melt() %>%
  ggplot(aes(subj, value, fill = variable)) +
  
  geom_col(position = position_dodge(width = 0.5), width = 0.5) +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "cuedts")





stern.er <- stern %>% filter(!subj %in% names(is.missing.fmri)[is.missing.fmri])

stern.er %>%
  
  group_by(subj, session) %>%
  
  mutate(
    er.o = as.numeric(is.na(resp)),
    er.c = ifelse(is.na(resp), 0, 1 - acc)
    ) %>%
  
  summarize(across(c("er.o", "er.c"), mean)) %>%
  
  reshape2::melt() %>%
  ggplot(aes(subj, value, fill = variable)) +
  
  geom_col(position = position_dodge(width = 0.5), width = 0.5) +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "stern")




stroop.er <- stroop %>% filter(!subj %in% names(is.missing.fmri)[is.missing.fmri], acc.final != "unintelligible")

stroop.er %>%
  
  group_by(subj, session) %>%
  
  mutate(
    er.o = as.numeric(acc.final == "no.response"),
    er.c = ifelse(as.numeric(acc.final == "no.response"), 0, 1 - acc)
    ) %>%
  
  summarize(across(c("er.o", "er.c"), mean)) %>%
  
  reshape2::melt() %>%
  ggplot(aes(subj, value, fill = variable)) +
  
  geom_col(position = position_dodge(width = 0.5), width = 0.5) +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "stroop")


```

* 197449 has over 60 percent response omission in Axcpt baseline, on both the cue response and probe response. Their response omission in baseline is also the highest among all subjs all sessions for Stroop and Cuedts (>0.3 for cts, >0.15 for stroop).
* 203418 "flipped" response mappings in Axcpt baseline
* 160830 quite high Stroop reactive omission (>0.15)

```{r}

axcpt[subj == 203418 & session == "baseline", c("cue.acc", "target.acc", "trialacc")] <-
  1 - axcpt[subj == 203418 & session == "baseline", c("cue.acc", "target.acc", "trialacc")]

axcpt.er <- axcpt %>% filter(!subj %in% names(is.missing.fmri)[is.missing.fmri])


```



## summary stats

```{r}

axcpt.er.sum <- axcpt.er %>%
  
  filter(trial.type %in% c("BX", "BY")) %>%
  
  group_by(subj, session, trial.type) %>%
  summarize(er = mean(1 - target.acc)) %>%
  
  pivot_wider(names_from = "trial.type", values_from = "er") %>%
  rename(hi = BX, lo = BY) %>%
  mutate(hilo = hi - lo)

cuedts.er.sum <- cuedts.er %>%
  
  filter(incentive == "Inc") %>%
  
  group_by(subj, session, trial.type) %>%
  summarize(er = mean(1 - acc)) %>%
  
  pivot_wider(names_from = "trial.type", values_from = "er") %>%
  rename(hi = InCon, lo = Con) %>%
  mutate(hilo = hi - lo)

stern.er.sum <- stern.er %>%
  
  filter(load01.trial.type %in% c("LL5RN", "LL5NN")) %>%
  
  group_by(subj, session, trial.type) %>%
  summarize(er = mean(1 - acc)) %>%
  
  pivot_wider(names_from = "trial.type", values_from = "er") %>%
  rename(hi = RN, lo = NN) %>%
  mutate(hilo = hi - lo)

stroop.er.sum <- stroop.er %>%
  
  filter(pc == "bias") %>%
  
  group_by(subj, session, trial.type) %>%
  summarize(er = mean(1 - acc)) %>%
  
  pivot_wider(names_from = "trial.type", values_from = "er") %>%
  rename(hi = InCon, lo = Con) %>%
  mutate(hilo = hi - lo)


```




# RT

## initial models


```{r}


## axcpt

axcpt.rt <- axcpt %>% 
  filter(
    !subj %in% names(is.missing.fmri)[is.missing.fmri], 
    trialacc == 1, target.rt > 0, cue.rt > 0
    )

axcpt.rt %>%
  
  group_by(subj, session) %>%

  select(session, subj, target.rt, cue.rt) %>%
  reshape2::melt() %>%
  
  ggplot(aes(subj, value, fill = variable)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5) +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "axcpt raw, all trials")


axcpt.rt.hilo <- axcpt.rt %>% filter(trial.type %in% c("BX", "BY"))

m.axcpt.rt0 <- lmer(
  target.rt ~ 0 + interaction(trial.type, session) + (0 + interaction(trial.type, session) | subj), 
  axcpt.rt.hilo,
  control = lmerControl(optimizer = "bobyqa")
)
axcpt.rt.hilo$resid <- resid(m.axcpt.rt0)
axcpt.rt.hilo$is.farout <- farout(axcpt.rt.hilo$resid)

sum(axcpt.rt.hilo$is.farout)
sum(axcpt.rt.hilo$is.farout) / nrow(axcpt.rt.hilo)

axcpt.rt.hilo %>%
  
  group_by(subj, session) %>%

  select(session, subj, resid) %>%
  ggplot(aes(subj, resid)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "axcpt resid, BXBY")

axcpt.rt.hilo %>%
  
  group_by(subj, session) %>%
  
  filter(!is.farout) %>%
  select(session, subj, target.rt) %>%
  ggplot(aes(subj, target.rt)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "axcpt raw, bxby, no farout")

## cuedts

cuedts.rt <- cuedts %>% 
  filter(
    !subj %in% names(is.missing.fmri)[is.missing.fmri], 
    acc == 1, rt > 0
    )

cuedts.rt %>%
  
  group_by(subj, session) %>%

  ggplot(aes(subj, rt)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "cuedts raw, all trials")

cuedts.rt.hilo <- cuedts.rt %>% filter(incentive == "Inc")

m.cuedts.rt0 <- lmer(
  rt ~ 0 + interaction(trial.type, session) + (0 + interaction(trial.type, session) | subj), 
  cuedts.rt.hilo,
  control = lmerControl(optimizer = "bobyqa")
)
cuedts.rt.hilo$resid <- resid(m.cuedts.rt0)
cuedts.rt.hilo$is.farout <- farout(cuedts.rt.hilo$resid)

sum(cuedts.rt.hilo$is.farout)
sum(cuedts.rt.hilo$is.farout) / nrow(cuedts.rt.hilo)

cuedts.rt.hilo %>%

  group_by(subj, session) %>%
  
  filter(!is.farout) %>%
  select(session, subj, rt) %>%
  ggplot(aes(subj, rt)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "cuedts raw, incentive, no farout")





## stern

stern.rt <- stern %>% 
  filter(
    !subj %in% names(is.missing.fmri)[is.missing.fmri], 
    acc == 1, rt > 0
    )

stern.rt %>%
  
  group_by(subj, session) %>%

  ggplot(aes(subj, rt)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "stern raw, all trials")

stern.rt.hilo <- stern.rt %>% filter(load01.trial.type %in% c("LL5RN", "LL5NN"))

m.stern.rt0 <- lmer(
  rt ~ 0 + interaction(trial.type, session) + (0 + interaction(trial.type, session) | subj), 
  stern.rt.hilo,
  control = lmerControl(optimizer = "bobyqa")
)
stern.rt.hilo$resid <- resid(m.stern.rt0)
stern.rt.hilo$is.farout <- farout(stern.rt.hilo$resid)

sum(stern.rt.hilo$is.farout)
sum(stern.rt.hilo$is.farout) / nrow(stern.rt.hilo)

stern.rt.hilo %>%
  
  group_by(subj, session) %>%

  select(session, subj, resid) %>%
  ggplot(aes(subj, resid)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "stern resid, ll5")

stern.rt.hilo %>%
  
  group_by(subj, session) %>%
  
  filter(!is.farout) %>%
  select(session, subj, rt) %>%
  ggplot(aes(subj, rt)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "stern raw, ll5, no farout")





## stroop

stroop.rt <- stroop %>% 
  filter(
    !subj %in% names(is.missing.fmri)[is.missing.fmri], 
    acc == 1, rt > 0, !is.na(rt)
    )

stroop.rt %>%
  
  group_by(subj, session) %>%

  ggplot(aes(subj, rt)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "stroop raw, all trials")

stroop.rt.hilo <- stroop.rt %>% filter(pc == "bias")

m.stroop.rt0 <- lmer(
  rt ~ 0 + interaction(trial.type, session) + (0 + interaction(trial.type, session) | subj), 
  stroop.rt.hilo,
  control = lmerControl(optimizer = "bobyqa")
)
stroop.rt.hilo$resid <- resid(m.stroop.rt0)
stroop.rt.hilo$is.farout <- farout(stroop.rt.hilo$resid)

sum(stroop.rt.hilo$is.farout)
sum(stroop.rt.hilo$is.farout) / nrow(stroop.rt.hilo)

stroop.rt.hilo %>%
  
  group_by(subj, session) %>%

  select(session, subj, resid) %>%
  ggplot(aes(subj, resid)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "stroop resid, bias")

stroop.rt.hilo %>%
  
  group_by(subj, session) %>%
  
  filter(!is.farout) %>%
  select(session, subj, rt) %>%
  ggplot(aes(subj, rt)) +
  
  geom_boxplot(position = position_dodge(width = 0.5), width = 0.5, fill = "grey40") +
  facet_grid(vars(session)) +
  
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "top") +
  labs(title = "stroop raw, bias, no farout")



```

## models on trimmed data

```{r}

m.axcpt.rt1  <- update(m.axcpt.rt0, data = axcpt.rt.hilo[is.farout == FALSE])
m.cuedts.rt1 <- update(m.cuedts.rt0, data = cuedts.rt.hilo[is.farout == FALSE])
m.stern.rt1  <- update(m.stern.rt0, data = stern.rt.hilo[is.farout == FALSE])
m.stroop.rt1 <- update(m.stroop.rt0, data = stroop.rt.hilo[is.farout == FALSE])

lapply(
  list(Axcpt = m.axcpt.rt1, Cuedts = m.cuedts.rt1, Stern = m.stern.rt1, Stroop = m.stroop.rt1),
  summary
)

# lapply(
#   list(Axcpt = m.axcpt.rt1, Cuedts = m.cuedts.rt1, Stern = m.stern.rt1, Stroop = m.stroop.rt1),
#   function(x) coef(x)$subj
# )

```


## summary stats

```{r}

axcpt.rt.sum <- axcpt.rt.hilo[is.farout == FALSE] %>%
  
  group_by(subj, session, trial.type) %>%
  summarize(rt = mean(target.rt)) %>%
  
  pivot_wider(names_from = "trial.type", values_from = "rt") %>%
  rename(hi = BX, lo = BY) %>%
  mutate(hilo = hi - lo)

cuedts.rt.sum <- cuedts.rt.hilo[is.farout == FALSE] %>%
  
  group_by(subj, session, trial.type) %>%
  summarize(rt = mean(rt)) %>%
  
  pivot_wider(names_from = "trial.type", values_from = "rt") %>%
  rename(hi = InCon, lo = Con) %>%
  mutate(hilo = hi - lo)

stern.rt.sum <- stern.rt.hilo[is.farout == FALSE] %>%
  
  group_by(subj, session, trial.type) %>%
  summarize(rt = mean(rt)) %>%
  
  pivot_wider(names_from = "trial.type", values_from = "rt") %>%
  rename(hi = RN, lo = NN) %>%
  mutate(hilo = hi - lo)


stroop.rt.sum <- stroop.rt.hilo[is.farout == FALSE] %>%
  
  group_by(subj, session, trial.type) %>%
  summarize(rt = mean(rt)) %>%
  
  pivot_wider(names_from = "trial.type", values_from = "rt") %>%
  rename(hi = InCon, lo = Con) %>%
  mutate(hilo = hi - lo)


```

# cross-task correlations



## summary stats

* numbers on upper triangle are rank correlation


### RT

```{r fig.width = 7}

## focus only on complete cases

axcpt.rt.sum  %<>% filter(subj %in% subjs.complete)
cuedts.rt.sum %<>% filter(subj %in% subjs.complete)
stern.rt.sum  %<>% filter(subj %in% subjs.complete)
stroop.rt.sum %<>% filter(subj %in% subjs.complete)

axcpt.rt.sum.w <- axcpt.rt.sum %>% select(-lo, -hi) %>% pivot_wider(names_from = "session", values_from = "hilo")
cuedts.rt.sum.w <- cuedts.rt.sum %>% select(-lo, -hi) %>% pivot_wider(names_from = "session", values_from = "hilo")
stern.rt.sum.w <- stern.rt.sum %>% select(-lo, -hi) %>% pivot_wider(names_from = "session", values_from = "hilo")
stroop.rt.sum.w <- stroop.rt.sum %>% select(-lo, -hi) %>% pivot_wider(names_from = "session", values_from = "hilo")


## baseline
panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- cor(x, y, use = "complete.obs", method = "spearman")
    txt <- format(c(r, 0.123456789), digits = digits)[1]
    txt <- paste0(prefix, txt)
    if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * abs(r))
}
panel.hist <- function(x, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(usr[1:2], 0, 1.5) )
    h <- hist(x, plot = FALSE)
    breaks <- h$breaks; nB <- length(breaks)
    y <- h$counts; y <- y/max(y)
    rect(breaks[-nB], 0, breaks[-1], y, col = "cyan", ...)
}


pairs(
  cbind(
    Axcpt = axcpt.rt.sum.w$baseline, Cuedts = cuedts.rt.sum.w$baseline, 
    Stern = stern.rt.sum.w$baseline, Stroop = stroop.rt.sum.w$baseline
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "baseline"
)

## proactive

pairs(
  cbind(
    Axcpt = axcpt.rt.sum.w$proactive, Cuedts = cuedts.rt.sum.w$proactive, 
    Stern = stern.rt.sum.w$proactive, Stroop = stroop.rt.sum.w$proactive
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "proactive"
)

## reactive

pairs(
  cbind(
    Axcpt = axcpt.rt.sum.w$reactive, Cuedts = cuedts.rt.sum.w$reactive, 
    Stern = stern.rt.sum.w$reactive, Stroop = stroop.rt.sum.w$reactive
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "reactive"
)


```



### error

```{r, fig.width = 7}

## focus only on complete cases

axcpt.er.sum  %<>% filter(subj %in% subjs.complete)
cuedts.er.sum %<>% filter(subj %in% subjs.complete)
stern.er.sum  %<>% filter(subj %in% subjs.complete)
stroop.er.sum %<>% filter(subj %in% subjs.complete)

axcpt.er.sum.w <- axcpt.er.sum %>% select(-lo, -hi) %>% pivot_wider(names_from = "session", values_from = "hilo")
cuedts.er.sum.w <- cuedts.er.sum %>% select(-lo, -hi) %>% pivot_wider(names_from = "session", values_from = "hilo")
stern.er.sum.w <- stern.er.sum %>% select(-lo, -hi) %>% pivot_wider(names_from = "session", values_from = "hilo")
stroop.er.sum.w <- stroop.er.sum %>% select(-lo, -hi) %>% pivot_wider(names_from = "session", values_from = "hilo")


## baseline

pairs(
  cbind(
    Axcpt = axcpt.er.sum.w$baseline, Cuedts = cuedts.er.sum.w$baseline, 
    Stern = stern.er.sum.w$baseline, Stroop = stroop.er.sum.w$baseline
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "baseline"
)

## proactive

pairs(
  cbind(
    Axcpt = axcpt.er.sum.w$proactive, Cuedts = cuedts.er.sum.w$proactive, 
    Stern = stern.er.sum.w$proactive, Stroop = stroop.er.sum.w$proactive
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "proactive"

)

## reactive

pairs(
  cbind(
    Axcpt = axcpt.er.sum.w$reactive, Cuedts = cuedts.er.sum.w$reactive, 
    Stern = stern.er.sum.w$reactive, Stroop = stroop.er.sum.w$reactive
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "reactive"

)



```

## combined 

```{r}


axcpt.comp.sum.w <- full_join(
  axcpt.rt.sum %>% transmute(hilo.rt = hi/lo),
  axcpt.er.sum %>% transmute(hilo.er = (1-hi)/(1-lo))
  ) %>%
  transmute(hilo = hilo.rt / hilo.er) %>% 
  pivot_wider(names_from = "session", values_from = "hilo")

cuedts.comp.sum.w <- full_join(
  cuedts.rt.sum %>% transmute(hilo.rt = hi/lo),
  cuedts.er.sum %>% transmute(hilo.er = (1-hi)/(1-lo))
  ) %>%
  transmute(hilo = hilo.rt / hilo.er) %>% 
  pivot_wider(names_from = "session", values_from = "hilo")

stern.comp.sum.w <- full_join(
  stern.rt.sum %>% transmute(hilo.rt = hi/lo),
  stern.er.sum %>% transmute(hilo.er = (1-hi)/(1-lo))
  ) %>%
  transmute(hilo = hilo.rt / hilo.er) %>% 
  pivot_wider(names_from = "session", values_from = "hilo")

stroop.comp.sum.w <- full_join(
  stroop.rt.sum %>% transmute(hilo.rt = hi/lo),
  stroop.er.sum %>% transmute(hilo.er = (1-hi)/(1-lo))
  ) %>%
  transmute(hilo = hilo.rt / hilo.er) %>% 
  pivot_wider(names_from = "session", values_from = "hilo")


pairs(
  cbind(
    Axcpt = axcpt.comp.sum.w$baseline, Cuedts = cuedts.comp.sum.w$baseline, 
    Stern = stern.comp.sum.w$baseline, Stroop = stroop.comp.sum.w$baseline
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "baseline"
)

## proactive

pairs(
  cbind(
    Axcpt = axcpt.comp.sum.w$proactive, Cuedts = cuedts.comp.sum.w$proactive, 
    Stern = stern.comp.sum.w$proactive, Stroop = stroop.comp.sum.w$proactive
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "proactive"

)

## reactive

pairs(
  cbind(
    Axcpt = axcpt.comp.sum.w$reactive, Cuedts = cuedts.comp.sum.w$reactive, 
    Stern = stern.comp.sum.w$reactive, Stroop = stroop.comp.sum.w$reactive
    ),
  pch = 16,
  upper.panel = panel.cor,
  diag.panel = panel.hist,
  main = "reactive"

)


```



## HLM

### RT

### error


# write

```{r}

error.sum <- bind_rows(
  Axcpt = axcpt.er.sum.w,
  Cuedts = cuedts.er.sum.w,
  Stern = stern.er.sum.w,
  Stroop = stroop.er.sum.w,
  .id = "task"
)

rt.sum <- bind_rows(
  Axcpt = axcpt.rt.sum.w,
  Cuedts = cuedts.rt.sum.w,
  Stern = stern.rt.sum.w,
  Stroop = stroop.rt.sum.w,
  .id = "task"
)


fwrite(error.sum, here("out", "behav_sumstat_error.csv"))
fwrite(rt.sum, here("out", "behav_sumstat_rt.csv"))

```








<!-- ### error -->




<!-- ```{r} -->

<!-- ## initial models -->

<!-- axcpt.er <- axcpt %>% filter( -->
<!--   subj %in% dimnames(a)$subj, cue.acc == 1, -->
<!--   session == "baseline", trial.type %in% c("BX", "BY") -->
<!-- ) %>% -->
<!--   mutate(trial.type = relevel(as.factor(trial.type), "BY")) -->

<!-- m.axcpt0.er <- glmer( -->
<!--   1-target.acc ~ trial.type + (trial.type | subj), -->
<!--   axcpt.er, -->
<!--   family = "binomial" -->
<!--   # control = lmerControl(optimizer = "bobyqa") -->
<!-- ) -->
<!-- summary(m.axcpt0.er) -->

<!-- cuedts.er <- cuedts %>% filter( -->
<!--   subj %in% dimnames(a)$subj, -->
<!--   session == "baseline" -->
<!-- ) -->

<!-- m.cuedts0.er <- glmer( -->
<!--   1-acc ~ trial.type + (trial.type | subj), -->
<!--   cuedts.er, -->
<!--   family = "binomial" -->
<!--   # control = lmerControl(optimizer = "bobyqa") -->
<!-- ) -->
<!-- summary(m.cuedts0.er) -->

<!-- stern.er <- stern %>% filter( -->
<!--   subj %in% dimnames(a)$subj, -->
<!--   session == "baseline", load01 == "LL5", trial.type %in% c("RN", "NN") -->
<!-- ) -->

<!-- m.stern0.er <- glmer( -->
<!--   1-acc ~ trial.type + (trial.type | subj), -->
<!--   stern.er, -->
<!--   family = "binomial" -->
<!--   # control = lmerControl(optimizer = "bobyqa") -->
<!-- ) -->
<!-- summary(m.stern0.er) -->

<!-- stroop.er <- stroop %>% filter( -->
<!--   subj %in% dimnames(a)$subj, -->
<!--   pc == "bias", -->
<!--   session == "baseline" -->
<!-- ) -->

<!-- m.stroop0.er <- glmer( -->
<!--   1-acc ~ trial.type + (trial.type | subj), -->
<!--   stroop.er, -->
<!--   family = "binomial" -->
<!--   # control = lmerControl(optimizer = "bobyqa") -->
<!-- ) -->
<!-- summary(m.stroop0.er) -->

<!-- # mod <- m.stroop0.er -->

<!-- get.error.rate <- function(mod, newname) { -->

<!--   d <- data.frame( -->
<!--     subj = rownames(coef(mod)$subj), -->
<!--     er.logit.stroop = coef(mod)$subj[, 2],  ## extract logits -->
<!--     er.logit.congr  = coef(mod)$subj[, 1] -->
<!--   ) %>% -->
<!--     mutate( -->
<!--       er.logit.incon = er.logit.stroop + er.logit.congr,  ## logit of error on incon trials -->
<!--       ##  blup stroop effect in units percent error: -->
<!--       stroop.er = (logit2prob(er.logit.incon) - logit2prob(er.logit.congr)) * 100 -->
<!--     ) %>% -->
<!--     dplyr::select(subj, er = stroop.er) -->

<!--   d[, 2] -->

<!-- } -->

<!-- logit2prob <- function(x) exp(x) / (1 + exp(x)) -->


<!-- er <- data.frame( -->
<!--   Axcpt  = get.error.rate(m.axcpt0.er), -->
<!--   Cuedts = get.error.rate(m.cuedts0.er), -->
<!--   Stern  = get.error.rate(m.stern0.er), -->
<!--   Stroop = get.error.rate(m.stroop0.er) -->
<!-- ) -->

<!-- cor(er) -->

<!-- ``` -->

